Multi-target detection with application to cryo-electron microscopy

### 2019-02-27 inverse_problems/inverse_problems.tex
cryo-EM model

\section{Introduction}

%\subsection{Problem formulation} \label{sec:problem_formulation}

@@

A 2-D micrograph $y$ can be in terms of~\eqref{eq:model} where the discrete signals $x_1,\ldots,x_K$ are replaced by a random signal drawn from the a general distribution. In particular, in each position $s[i]$, a 2-D tomographic projection of the 3-D structure is placed, taken from a random viewing direction according to (possibly unknown) fixed distribution.

>>>>

\section{Introduction} \label{sec:intro}

@@

A 2-D micrograph $y$ can be written in terms 
of the models described in Section~\ref{sec:intro} as
\begin{equation}  \label{eq:model_cryo}
y  =   s \ast x + \varepsilon,
\end{equation}
where tomographic projections are placed according to the signal $s$. In this model, the signal $x$ represents the 2-D tomographic projections of the 3-D structure taken from  random viewing directions according to (possibly unknown) distribution. In particular, by letting $V$ describes the underlying volume, $R_\omega$ a random 3-D rotation drawn from some unknown distribution and $P$ a tomographic projection, we have
\begin{equation}
x= P(R_\omega V).
\end{equation}
By allowing $V$ to be a random signal as well, this model can encode a mixture of structures  
(which might be continuous as well).
